The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-06-28 paper.tex
add a figure corresponding to fitrfi.jl

>>>>

\begin{figure*}[ht]
    \centering
    \begin{tabular}{cccc}
        \includegraphics[width=0.22\textwidth]{figures/smeared-images/before-component-removal-spw14} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-images/after-component-removal-spw14} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-images/rfi-like-component-spw14} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-images/pickup-like-component-spw14} \\
        \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} \\
    \end{tabular}
    \caption{
        This figure illustrates the process of fitting for terrestrial sources of correlated noise.
        Each image is of the entire visible hemisphere above the OVRO-LWA but the data has been
        averaged over the entire 28 hour observing period. Because of this Cas A and Cyg A are
        smeared along tracks of constant declination. These images are generated using WSCLEAN
        \citep{2014MNRAS.444..606O} \textbf{(a)} This image shows the initial data before any
        sources have been removed. \textbf{(b)} This image shows the final state after 3
        terrestrial sources of correlated noise have been removed. \textbf{(c)} This image
        illustrates the contribution of an RFI source towards the north-west that was removed by
        peeling. \textbf{(d)} This removed component is not associated with a dot on the horizon.
        Instead it is likely associated with common-mode pickup in the analog signal chain.
    }
\end{figure*}
